\chapter{Conclusion}\label{discussion}
An imaging system has been developed with special emphasis on the ability to measure bubbles close to the water surface and developing a robust bubble detection algorithm. The current setup can reliably detect bubbles with radii ranging from $110$\,$\mu$m to $500$\,$\mu$m.

\section{Summary}
\textbf{Measurement setup}: Artificially generated bubbles were lit from below, which resulted in images where bubbles are characterized by two peaks for low bubble concentrations, and images where bubbles had a more apparent curvature around the bubble edge for high bubble concentrations. Keeping the angle between the camera and the light source at 90$^\circ$ insured a consistent pattern across the different used water tanks. 

\textbf{Algorithm \ref{algo:bubbleNet}}: This algorithm uses a deep learning approach. So generating a large amount of annotated training data was necessary. This was achieved through simulation as well as through annotating measurement results with a logistic regression classifier, i.e. a simpler classifier was optimized to detect true positive bubble instances only, which were then used to train the convolutional neural network. This algorithm performed well when measured by the mAP@0.5IoU criterion. Also, the variation within the validation dataset was strong, therefore it has been verified that this algorithm is robust. Using a deep learning approach however, comes with an inherent limit, which is the lack of interpretability of the model. 

\textbf{Algorithm \ref{algo:bubbleCurves}}: Images with large bubble concentrations show bubbles with a nicely recognizable curvature. This observation was used in this algorithm to classify bubbles and determine their radii. For classification, features that extract orientation and edge's concavity from a potential bubble were used. The radius is then determined from the bubble's lower half. This algorithm performed slightly worse than algorithm \ref{algo:bubbleNet}. 
The validation dataset was also not as varied as the one used for the previous algorithm. Therefore, this algorithm is less robust against large changes in camera settings and lighting conditions. The advantage of this algorithm however, is that it can be easily interpreted since the features of the classifier were chosen manually. 

\textbf{Calibration}: It has been shown that the width of the brightest peak at the bubble's lower edge can be used to determine the bubble's depth, i.e.\ distance from the focal plane. As for the radius calibration, an additional light source was used to capture bubbles as dark circles, track them, compute their radii and then find a function that describes their radii with the ones computed with algorithms \ref{algo:bubbleNet} and \ref{algo:bubbleCurves}. In both calibration setups real bubbles were used, i.e. no calibration target that emulates bubbles was needed, which contributed positively to the calibration accuracy. 

\section{Outlook}
The evaluation criterion introduced in this work shows that the developed algorithms can be used reliably. A comparison of the bubble distributions computed with the proposed algorithm in this work with bubble distributions resulting from other methods is necessary to validate the developed bubble measuring technique as a whole. 

The optical experimental setup can be further improved to detect smaller bubbles by increasing the magnification factor, e.g.\ by using a lens with a larger focal length. Changing the experimental setup would require changing different hyperparameters of the algorithms such as maximum signal length for algorithm \ref{algo:bubbleNet} and the initial window size for algorithm \ref{algo:bubbleCurves}. However, re-training the classifiers would not be necessary. Furthermore, it is currently not possible to acquire measurements for more than a few minutes, because the light source would become too hot. Synchronizing the light source with the camera, e.g.\ with a triggering mechanism would eliminate this problem. 